\papertitle

### 2013-01-19 manuscript.tex
more edits to sections 4 and 5

Our model of the ground station comprises models of both the camera and the
pose estimation computation. The camera model contains both a latency, which 
is in series with the path between the ``Camera'' and 
``Ornithopter Dynamics'' blocks in Figure~\ref{fig:block_diagram}, and a 
model of the camera's viewing angle constraints.

@@

The step response rise time is 1.4 seconds. The H$^2$Bird flies at an 
average forward velocity of 1.2 m/s during our experiments, so we estimate 
the minimum turning radius of the robot is 1.07 meters:
\begin{equation}
\label{eq:min_radius}
\begin{aligned}
\text{Minimum radius} & = \frac{360^{\circ}\times\text{Rise time}\times\text{Flight
speed}}{\text{Final angle}\times 2\pi}\\
& = \frac{360^{\circ}\times 1.4s\times 1.2\frac{m}{s}}{90^{\circ}\times2*\pi} = 1.07 m
\end{aligned}
\end{equation}
In the experiments we present in this work, we choose a flight speed lower 
than the maximum speed of the ornithopter, to facilitate more robust 
tracking.

%............................................................................%
\subsubsection{Ground Station Pose Estimation}
To measure the capture latency of the camera, we wrote a simple test 
application which draws a large colored rectangle on the ground station's 
screen, then uses the camera to detect that changes in that rectangle's 
color. By noting the value of the system timer just before it changes the 
rectangle, and just after the camera detects that change, the application 
arrives at an estimate of the video capture pipeline latency. We averaged 
these result over several hundred rapidly-executed trials to determine the 
capture latency we used to model the system.

@@

We determine the backwards reachable set of initial states for successful 
narrow passage traversal both geometrically and using Monte Carlo simulation. 
(Figs.~\ref{fig:feasible_set} and~\ref{fig:heat_map}) In Figure ~\ref{fig:feasible_set}, 
the blue lines represent the camera viewing triangle, the black line represents the window, and the black 
dot represents the camera. For the initial conditions, we used a uniform
grid of 5 cm increments within the camera viewing region, and an initial
angular heading perpendicular to the window plane. A success, or feasible 
initial condition, consists of a path that intersects the window at some 
point and does not leave the camera viewing triangle, and is indicated in 
green. The geometrically infeasible region is computed using the minimum 
turning radius and the geometry of the camera's field-of-view and is 
indicated in blue. The region in red is not geometrically feasible, but is 
infeasible as a result of the cooperative control simulation dynamics.

We simulate the motion of the ornithopter beginning from various positional 
and angular heading initial conditions. We use this model, as determined 
through system identification (Sec.~\ref{sec:system_model}) using the 
cooperative control method in Figure~\ref{fig:block_diagram}.

We conducted a Monte Carlo simulation to determine the probability of 
successful window navigation for a given point within the testing area. 
Using this information we can make assumptions about ideal starting 
positions for cooperative control. For each point within a 10 cm grid within 
the camera viewing triangle, we simulated 40 trials using an initial heading 
randomly sampled from a uniform distribution between -90$^{\circ}$ and 
90$^{\circ}$. Figure~\ref{fig:heat_map} depicts the results of the Monte 
Carlo simulation.

@@

As the H$^2$Bird cannot detect the target on its own, we used cooperative 
control with the ground station, which to provided remote guidance to 
H$^2$Bird to allow it to navigate to the window. We used a motion capture 
system to record ground truth data. We present a sketch of this experimental 
setup in Figure~\ref{fig:experiment_cartoon}.

@@

Each trial included the following steps (see Fig.~\ref{fig:pf_screencap}):
\begin{enumerate}
\item We identify the window to the ground station by dragging a bounding 
box over it using the mouse. 
\item We release H$^2$Bird by hand, in view of the camera at the desired 
starting grid point.
\item The H$^2$Bird attempts to fly through the window with, with remote 
guidance from the ground station.
\end{enumerate}

After every 5 trials, we replaced the ornithopter's battery with a fully 
charged one.

In total, we collected 80 trials over a variety of starting positions. Our 
goal for these experiments was to verify the model described in 
Section~\ref{sec:system_model}, so we conducted 60 of the 80 trials in a 
grid along the edges of the camera view plane, and in 5 cm meter increments 
from the window, in an effort to determine the success rate on the edges of 
the testing space. We conducted 20 additional trials directly in front of 
the camera, to determine the success rate near the center of viewing plane.

@@

Conducting the experimental trials as described in 
Section~\ref{sec:experiments_verification}, we achieved a success rate of 
80\% for initial conditions in the middle of the testing space and in front 
of the camera. As we moved towards the edges of the feasible region in 
Figure~\ref{fig:flight_paths}, the success rate diminished to 50\%. We 
present the results of our experimental trials in Figures~\ref{fig:flight_paths} 
and~\ref{fig:flight_paths_feasible}.

The lower success rate on the edges of the camera frame is explained by 
several factors. On the edges of the viewing triangle, the yaw control 
inputs are large in magnitude, although this is not necessary in all cases. 
Since the control algorithm we are using has no notion of depth, it applies 
the same control input whether the ornithopter is close to the camera, where 
small changes in heading are adequate, or far away from the camera, where 
large changes in heading are necessary. Due to this phenomenon, the 
controller often over or under-compensates in certain regions, depending 
upon the PID tuning and the distance from the camera. Tracking noise can 
also cause passage negotiation to fail. Variations in the H$^2$Bird hand 
launch can cause the system to respond differently for similar initial 
conditions. In addition, we changed H$^2$Bird battery approximately every 5 
tests, adding more variation to the H$^2$Bird performance by affecting the 
motor power output.

>>>>

Our model of the ground station includes models for both the camera and the
pose estimation computation. The camera model contains both a latency, which 
is in series with the path between the ``Camera'' and 
``Ornithopter Dynamics'' blocks in Figure~\ref{fig:block_diagram}, and a 
model of the camera's viewing angle constraints.

@@

The step response rise time is 1.4 seconds. The H$^2$Bird flies at an 
average forward velocity of 1.2 m/s during our experiments, so we estimate 
the minimum turning radius of the robot to be 1.07 meters:
\begin{equation}
\label{eq:min_radius}
\begin{aligned}
\text{Minimum radius} & = \frac{360^{\circ}\times\text{Rise time}\times\text{Flight
speed}}{\text{Final angle}\times 2\pi}\\
& = \frac{360^{\circ}\times 1.4s\times 1.2\frac{m}{s}}{90^{\circ}\times2*\pi} = 1.07 m
\end{aligned}
\end{equation}
In the experiments we present in this work, we choose a flight speed lower 
than the maximum speed of the ornithopter, to facilitate more robust 
tracking.

%............................................................................%
\subsubsection{Ground Station Pose Estimation}
To measure the capture latency of the camera, we wrote a simple test
application which draws a large colored rectangle on the ground station's
screen, then uses the camera to detect the changes in the rectangle's color.
By noting the value of the system timer just before the rectangle changes
color and just after the camera detects the change, the application records
the estimate of the video capture pipeline latency. We averaged the result
over several hundred rapidly-executed trials to determine the capture latency
we used to model the system.

@@

We determine the backwards reachable set of initial states for successful
narrow passage traversal both geometrically and using Monte Carlo simulation.
We simulate the motion of the ornithopter beginning from various positional
and angular heading initial conditions. We use our model, as determined
through system identification as described in Section~\ref{sec:system_model},
using the cooperative control method in Figure~\ref{fig:block_diagram}. The
results are presented in Figures~\ref{fig:feasible_set}
and~\ref{fig:heat_map}.

In Figure ~\ref{fig:feasible_set}, 
the blue lines represent the camera viewing triangle, the black line represents the window, and the black 
dot represents the camera. For the initial conditions, we used a uniform
grid of 5 cm increments within the camera viewing region, and an initial
angular heading perpendicular to the window plane. A success, or feasible 
initial condition, consists of a path that intersects the window at some 
point and does not leave the camera viewing triangle, and is indicated in 
green. The geometrically infeasible region is computed using the minimum 
turning radius and the geometry of the camera's field-of-view and is 
indicated in blue. The region in red is not geometrically feasible, but is 
infeasible as a result of the cooperative control simulation dynamics.

We conducted a Monte Carlo simulation to determine the probability of
successful window navigation for a given point within the testing area. Using
this information we can make assumptions about ideal starting positions for
cooperative control. For each point within a 10 cm grid within the camera
viewing triangle, we simulated 40 trials using an initial heading randomly
sampled from a uniform distribution between -90$^{\circ}$ and 90$^{\circ}$,
with the 0$^{\circ}$ heading perpendicular to the window.
Figure~\ref{fig:heat_map} depicts the results of the Monte Carlo simulation.

@@

As the H$^2$Bird cannot detect the target on its own, we used cooperative 
control with the ground station, which provided remote guidance to 
H$^2$Bird to allow it to navigate through the window. We used a motion capture 
system to record ground truth data. We present a sketch of this experimental 
setup in Figure~\ref{fig:experiment_cartoon}.

@@

Each trial included the following steps (see Fig.~\ref{fig:pf_screencap}):
\begin{enumerate}
\item We identify the window to the ground station by dragging a bounding 
box over it using a mouse. 
\item We release H$^2$Bird by hand, in view of the camera at the desired 
starting grid point.
\item The H$^2$Bird attempts to fly through the window, with remote 
guidance from the ground station.
\end{enumerate}

Every 5 trials, we replaced the ornithopter's battery with a fully 
charged one.

We collected 80 trials over a variety of starting positions. Our 
goal for these experiments was to verify the model described in 
Section~\ref{sec:system_model}, so we conducted 60 of the 80 trials in a 
grid along the edges of the camera view plane, and in 5 cm increments 
from the window plane, in an effort to determine the success rate on the edges of 
the testing space. We conducted 20 additional trials directly in front of 
the camera, to determine the success rate near the center of viewing plane.

@@

Conducting the experimental trials as described in 
Section~\ref{sec:experiments_verification}, we achieved a success rate of 
80\% for initial conditions in the middle of the testing space and in front 
of the camera. As we moved towards the edges of the feasible region in 
Figure~\ref{fig:flight_paths}, the success rate diminished to 50\%.

The lower success rate on the edges of the camera frame can be explained by 
several factors. On the edges of the viewing triangle, the yaw control 
inputs are large in magnitude, although this is not necessary in all cases. 
Since the control algorithm we are using has no notion of depth, it applies 
the same control input whether the ornithopter is close to the camera, where 
small changes in heading are adequate, or far away from the camera, where 
large changes in heading are necessary. Due to this phenomenon, the 
controller often over or under-compensates in certain regions, depending 
upon the PID tuning and the distance from the camera. Tracking noise can 
also cause passage negotiation to fail. Variations in the H$^2$Bird hand 
launch can cause the system to respond differently for similar initial 
conditions. In addition, we changed H$^2$Bird battery approximately every 5 
tests, adding more variation to the H$^2$Bird performance by affecting the 
motor power output.
